### 2008-12-06 doc/sec/Sec_paper.tex
conclusion

\ \ \ \ The rest of this paper is organized as follows: Section 2
presents the ARC Grid middleware, especially the architecture of the
new version of ARC. Section 3 describes the solution for
cross-middleware authentication and single sign-on, including
implementations for bridging the mismatch in terms of authentication
and single sign-on. Section 4 discusses the related research, and
Section 5 presents conclusion.

@@

\begin{center}
\includegraphics[width=3.4063in,height=2.1417in]{Secpaper-img2.png}
\end{center}

@@

{\centering
Figure 2. SAML2.0 SSO profile in ARC
\par}

@@

\liststyleLv
\begin{enumerate}
\item The client uses the user agent interface to launches a http
request including the IdP name (to which the user belongs) to the
service side. The endpoint of the SP service is the same as that of the
other target services, except the last part of the endpoint is
{\textquotedblleft}saml2sp{\textquotedblright} which is specific for
pointing to the SP Service. Note that we use Identity Provider (IdP)
name here to simplify the IdP discovery process in order to avoid the
IdP discovery process, because we suppose that user who would access
the target services should better know where is he from initially.
\item The SP Service (Service Provider) searches the metadata (we use
the same metadata format defined in Shibboleth) and gets the location
of the single sign-on service (hosted in IdP) and also the location of
assertion consuming service (hosted in this SP itself) in order to
compose the SAML {\textless}\textit{samlp:AuthnRequest}{\textgreater}
message. Then SP Service issues this
{\textless}\textit{samlp:AuthnRequest}{\textgreater} message by using
its own X.509 certificate (Note in the SAML SSO profile, certificate is
still needed by IdP and SP) and sends back to user agent.
\item User agent sends the
{\textless}\textit{samlp:AuthnRequest}{\textgreater} message to
Identity Provider.
\item Identity Provider requires an act of authentication. The
authentication mechanism is outside of the SAML2.0 SSO profile.
Shibboleth IdP implementation chooses some login handler for
authentication. The current user agent implementation is compatible to
\textit{Username/Password} login handler of Shibboleth IdP. Through the
http protocol, user agent will feed IdP with the username/password
which has been given by the caller of user agent interface.
\item Once the authentication has been succeeded, the IdP issues a SAML
response including an encrypted (encrypted by destination
SP{\textquotesingle}s public key) SAML assertion, and then this SAML
response will be delivered by the user agent to the Service Provider. 
\item The SP Service verifies and checks the SAML response, and decrypts
and stores the SAML assertion into session/connection context. The SAML
assertion includes the
{\textless}\textit{saml:AuthnStatement}{\textgreater} and
{\textless}\textit{saml:AttributeStatement}{\textgreater}.
\item The WS client launches the Grid/Web Service request via the same
connection as the one which is used by user agent to contact SP
Service.
\item The Grid/Web Service checks the
{\textless}\textit{saml:AuthnStatement}{\textgreater} from the session
context to see if the session is still valid through the
\textit{SecHandler} called {\textquotedblleft}\textit{SAML
SecHandler}{\textquotedblright}. If valid, service handles the service
processing and returns the response to WS client. Note that service
requires that WS client is from the same connection as the one on which
user agent contact SP service, in order to guarantee that the validity
of SSO profile result effects the WS client/Web Service interaction.
\end{enumerate}
\ \ \ \ The SP service and functional service(s) are hosted by the same
container, and they use the same X.509 credential. The client
authentication is switched off, so that client doesn{\textquotesingle}t
need to use any X.509 credential. Only the trusted certificates (CA
certificates for both SP and IdP) need to be configured for client side
so that SP and IdP can authenticate themselves to the client. As
required by SAML2.0 profile, the SP and IdP should have trust
relationship to each other.

@@

@@

\begin{center}
\includegraphics[width=4.1866in,height=2.7874in]{Secpaper-img6.png}
\end{center}
\begin{center}
\includegraphics[width=6.9252in,height=0.0161in]{Secpaper-img7.png}
\end{center}
\begin{center}
\includegraphics[width=6.9252in,height=0.0161in]{Secpaper-img8.png}
\end{center}
{\centering
Figure 6. SAML Token delegation service
\par}

@@

\begin{center}
\includegraphics[width=4.2957in,height=2.2575in]{Secpaper-img9.png}
\end{center}

@@

{\centering
\ \ \ \ \ \ \ \ \ Figure 7. SOAP message header with SAML delegation
token inside
\par}

@@

Similar work that integrates Shibboleth and Grid middleware does exist.
GridShib[17][18] uses Shibboleth to get entity{\textquotesingle}s
attribute for the authorization of services developed in Globus Tookit.
Unlike the work of this paper, GridShib does not use
Shibboleth{\textquotesingle}s native login handlers for authentication
to Shibboleth IdP, instead, a new login handler specific for X.509
based authentication is developed for Shibboleth IdP, and a credential
service is developed for acting as an online-CA, authenticating the
user, and issuing short-lived X.509 credential.

@@

>>>>

\ \ \ \ The rest of this paper is organized as follows: Section 2
presents the ARC Grid middleware, especially the architecture of the
new version of ARC. Section 3 describes the solution for
cross-middleware authentication and single sign-on, including
implementations for bridging the mismatch in terms of authentication
and single sign-on. Section 4 discusses the related research, and
Section 5 presents conclusion and future work.

@@

@@

\begin{center}
\includegraphics[width=3.2256in,height=1.8472in]{Secpaper-img2.png}
\end{center}
{\centering
Figure 2. SAML2.0 SSO profile in ARC
\par}

@@

\liststyleLv
\begin{enumerate}
\item The client uses the user agent interface to launches a http
request including the IdP name (to which the user belongs) to the
service side. The endpoint of the SP service is the same as that of the
other target services, except the last part of the endpoint is
{\textquotedblleft}saml2sp{\textquotedblright} which is specific for
pointing to the SP Service. Note that we use Identity Provider (IdP)
name here to simplify the IdP discovery process in order to avoid the
IdP discovery process, because we suppose that user who would access
the target services should better know where is he from initially.
\item The SP Service (Service Provider) searches the metadata (we use
the same metadata format defined in Shibboleth) and gets the location
of the single sign-on service (hosted in IdP) and also the location of
assertion consuming service (hosted in this SP itself) in order to
compose the SAML {\textless}\textit{samlp:AuthnRequest}{\textgreater}
message. Then SP Service issues this
{\textless}\textit{samlp:AuthnRequest}{\textgreater} message by using
its own X.509 certificate (Note in the SAML SSO profile, certificate is
still needed by IdP and SP) and sends back to user agent.
\item User agent sends the
{\textless}\textit{samlp:AuthnRequest}{\textgreater} message to
Identity Provider.
\item Identity Provider requires an act of authentication. The
authentication mechanism is outside of the SAML2.0 SSO profile.
Shibboleth IdP implementation chooses some login handler for
authentication. The current user agent implementation is compatible to
\textit{Username/Password} login handler of Shibboleth IdP. Through the
http protocol, user agent will feed IdP with the username/password
which has been given by the caller of user agent interface.
\item Once the authentication has been succeeded, the IdP issues a SAML
response including an encrypted (encrypted by destination
SP{\textquotesingle}s public key) SAML assertion, and then this SAML
response will be delivered by the user agent to the Service Provider. 
\item The SP Service verifies and checks the SAML response, and decrypts
and stores the SAML assertion into session/connection context. The SAML
assertion includes the
{\textless}\textit{saml:AuthnStatement}{\textgreater} and
{\textless}\textit{saml:AttributeStatement}{\textgreater}.
\item The WS client launches the Grid/Web Service request via the same
connection as the one which is used by user agent to contact SP
Service.
\item The Grid/Web Service checks the
{\textless}\textit{saml:AuthnStatement}{\textgreater} from the session
context to see if the session is still valid through the
\textit{SecHandler} called {\textquotedblleft}\textit{SAML
SecHandler}{\textquotedblright}. If valid, service handles the service
processing and returns the response to WS client. Note that service
requires that WS client is from the same connection as the one on which
user agent contact SP service, in order to guarantee that the validity
of SSO profile result effects the WS client/Web Service interaction.
\end{enumerate}
\ \ \ \ The SP service and other functional service(s) are hosted by the
same container, and they use the same X.509 credential. The client
authentication is switched off, so that client doesn{\textquotesingle}t
need to use any X.509 credential. Only the trusted certificates (CA
certificates for both SP and IdP) need to be configured for client side
so that SP and IdP can authenticate themselves to the client. As
required by SAML2.0 profile, the SP and IdP should have trust
relationship to each other.

@@

\ \ \ It is worth mentioning is: since the SLCS X.509 credential or
delegated credential can be used to issue X.509 token, \ the X.509
credential delegation and SAML Token delegation are smoothly bridged,
which benefits the single sign-on.

@@

\begin{center}
\includegraphics[width=4.0016in,height=2.639in]{Secpaper-img6.png}
\end{center}
\begin{center}
\includegraphics[width=6.9252in,height=0.0161in]{Secpaper-img7.png}
\end{center}
\begin{center}
\includegraphics[width=6.9252in,height=0.0161in]{Secpaper-img8.png}
\end{center}
{\centering
Figure 6. SAML Token delegation service
\par}

@@

@@

\begin{center}
\includegraphics[width=3.8374in,height=1.9063in]{Secpaper-img9.png}
\end{center}
{\centering
\ \ \ \ \ \ \ \ \ Figure 7. SOAP message header with SAML delegation
token inside
\par}

@@

Similar work that integrates Shibboleth and Grid middleware does exist.
GridShib[17][18] uses Shibboleth to get entity{\textquotesingle}s
attribute for the authorization of services developed in Globus Tookit.
Unlike the work of this paper, GridShib does not use
Shibboleth{\textquotesingle}s native login handlers for authentication
to Shibboleth IdP, instead, a new login handler specific for X.509
based authentication is developed for Shibboleth IdP, and a credential
service is developed for acting as an online-CA, authenticating the
user, and issuing short-lived X.509 credential. Moreover, this paper
provides a single sign-on solution for user authenticating to Grid
services by directly using SAML2.0 SSO profile (section 3.1).

@@

\ \ \ \ Within this paper we presented the solution inside ARC Grid
middleware towards the cross-middleware authentication and single
sing-on. The goal of our work is to develop an interoperatable and
accessible single sign-on solution to be used for VO scenario in
production Grids, where users can easily authenticate against the Grids
with any of his credentials (not only X.509 credential) from anywhere,
and travel inside Grid middleware boundaries and even across
heterogeneous Grids middleware boundaries, \ without re-authentication
in a reasonable period. In order to do so, we implemented some standard
based Web Services (including SLCS service, X.509 credential delegation
service, and SAML Token delegation service), as well as the user agent
and Service Provider in context of SAML2 SSO profile.

\ \ \ It must be noted that due to standard specifications utilized
(SAML and WS-Security) which are independent from any particular
middleware, though the WS clients and Web/Grid Services presented in
this paper are mostly developed on ARC middleware, they can
interoperate with WS clients and Web/Grid Services developed on any
other middlware in a standardized way. ARC also supports
interoperability with Grid middlewares that require GSI based
communication.

\ \ \ \ Since authorization is also a key problem for VO, as the future
work, we will implement a solution for cross-middleware authorization
by using the standard specification such as SAML.
